---
title       : DDP - Course Project
subtitle    : Filtering mt-cars data on the fly
author      : wally_holly
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---.class1

## Goal of the app

My little shiny app allows it to filter the mtcars dataset on the fly.

1. The user enters the number of cylinders of a car.
2. The user specify the lower and upper limit of the mpg value (Miles/(US) gallon)
3. The app selects all cars from the data set that fulfill the criteria, selected by the user. 

---.class #id

## The data set
- Data Set: mtcars
- extracted from the 1974 Motor Trend US magazine
- 32 cars; 11 variables:
```{r}
names(mtcars)
```

---

## A quick look on the data
```{r}
head(mtcars)
```

---

## Table of the cars by number of cylinders
```{r, echo=FALSE}
a<-as.data.frame(table(mtcars$cyl))
colnames(a)<-c("No. of cylinders","frequency")
print(a)
```
We can see that there are 11 cars with 4 cylinders, 7 cars with 6 cylinders and 14 models with 8 cylinders

---

## Histogram of the cars by mileage
```{r, echo=FALSE}
hist(mtcars$mpg)
```

---
